---
title: "Dataframe-merging"
author: "Khusaal Giri"
date: "March 25, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Initializing the dataframes:
```{r}
total_values=3
a=c()
b=c()
c=c()
for(i in c(1:total_values)){
  a[i]=i-1
  b[i]=i-1
  c[i]=i-1
}
a=paste('A',a,sep='')
b=paste('B',b,sep='')
c=paste('C',c,sep='')
df1=data.frame(A=a,B=b)
df1
df2=data.frame(A=a,C=c)
df2
```

Paste command will paste the character before or after every element of the vector seperated by quotes.

To concat two dataframes in R,we need to have equal number of
columns in both the dataframes.So,appending extra columns in both
the dataframes & assigning it 'NA'
```{r}
df1_temp=df1
df1_temp$C <- NA
df1_temp
df2_temp=df2
df2_temp$B <- NA
df2_temp
```

Concatenating the dataframes along the rows(Vertically):
```{r}
not_so_good=rbind(df1_temp,df2_temp)
not_so_good
```

Concatenating the dataframes along the columns(Horizontally) and with repetition of the common column:
```{r}
much_better=cbind(df1,df2)
much_better
```

Concatenating the dataframes along the columns(Horizontally) without the repetition of the common column(Inner join):
```{r}
best_result=merge(df1,df2,by='A')
best_result
```
